Sediment transport capacity response to variations in water discharge in pressurized subglacial channels

### 2025-02-03 Delaneyetal2024.tex
Updates from Overleaf

The first numerical experiment aims to quantify the timing and covariance of the subglacial model outputs with respect to water discharge in response to different seasonal evolutions and peaks (Figure~\ref{fig:model_outs}).
Variable relationships between model outputs and water discharge emerge for the subaerial and subglacial cases as channel size evolves (Figure~\ref{fig:model_outs} a, e).
Because subaerial channels have no history dependence, each water discharge value in the subaerial channel produces a unique water velocity, shear stress, and width-integrated shear stress (Section~\ref{sect:sub_mode}).
This characteristic results in a perfect rank correlation between the variables and water discharge (Figure~\ref{fig:Qw_vari}).
An inconsistent relationship between subglacial model outputs and water discharge persists across the range of parameters examined in the ensemble runs (see Section~\ref{sect:ensemble}; Figure S15).
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=0.75\linewidth]{Fig2.png}
  \caption{Model outputs from simulations using the hydrographs in panels a and e for the scenarios \alpine{} (a-d) and \icesheet{} (e-h).
    Black (gray) lines in a and e represent the subglacial channel size (water discharge).
    Blue (orange) lines represent outputs from the subglacial (subaerial) channel.
    Data are shown at $15$\unit{min} intervals.
    Arrows show examples where variables peak in the subglacial channel before the subaerial one.
    Insets in f-h show the peak melt event denoted by the shaded area in panels e--h, with 
  }
  \label{fig:model_outs}
\end{figure}

@@

\begin{acknowledgements}
  SNSF Project No. $\mathrm{PZ00P2}$\_$202024$ provided  funding for I. Delaney.
  A. Tedstone acknowledges funding from the European Research Council, award $818994$ -- CASSANDRA.
  G. King and M. J. Gevers provided useful comments on a previous version of this manuscript.
  We benefited from fruitful discussions with J. Irving.
  We thank B. Hubbard and an anonymous reviewer for constructive and critical comments on the manuscript.
\end{acknowledgements}
\bibliographystyle{copernicus}
\bibliography{Paperlib.bib}

>>>>

The first numerical experiment aims to quantify the sources of increased variability in the subglacial model outputs as they exhibit different seasonal evolutions and peaks (Figure~\ref{fig:model_outs}).
Variable relationships between model outputs and water discharge emerge for the subaerial and subglacial cases as channel size evolves (Figure~\ref{fig:model_outs} a, e).
Because subaerial channels have no history dependence, each water discharge value in the subaerial channel produces a unique water velocity, shear stress, and width-integrated shear stress (Section~\ref{sect:sub_mode}).
This characteristic results in a perfect rank correlation between the variables and water discharge (Figure~\ref{fig:Qw_vari}).
An inconsistent relationship between subglacial model outputs and water discharge persists across the range of parameters examined in the ensemble runs (see Section~\ref{sect:ensemble}; Figure S15).
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=0.75\linewidth]{Fig2.png}
  \caption{Model outputs from simulations using the hydrographs in panels a and e for the scenarios \alpine{} (a-d) and \icesheet{} (e-h).
    Black (gray) lines in a and e represent the subglacial channel size (water discharge).
    Blue (orange) lines represent outputs from the subglacial (subaerial) channel.
    Data are shown at $15$\unit{min} intervals.
    Arrows show examples where variables peak in the subglacial channel before the subaerial one.
    Insets in f-h show the peak melt event denoted by the shaded area in panels e--h, with 
  }
  \label{fig:model_outs}
\end{figure}

@@

\begin{acknowledgements}
  SNSF Project No. $\mathrm{PZ00P2}$\_$202024$ provided  funding for I. Delaney.
  A. Tedstone acknowledges funding from the European Research Council, award $818994$ -- CASSANDRA.
  G. King and M. J. Gevers provided useful comments on a previous version of this manuscript.
  We benefited from fruitful discussions with J. Irving.
  We thank two reviewers for constructive and critical comments on a previous version of the manuscript.
\end{acknowledgements}
\bibliographystyle{copernicus}
\bibliography{Paperlib.bib}
